---
title: "Visulization1"
author: "Yatong Feng"
date: "10/9/2020"
output: html_document
---

```{r}
library(tidyverse)
library(ggridges)
```

## load the weather data 
```{r, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

## scatterplot

Create my first scatterplot ever.

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) + 
  geom_point()
```

New approach, same plot

```{r}
weather_df %>% 
  ggplot(aes(tmin, tmax)) +
  geom_point()
```

save and edit a plot object

```{r}
plot_weather = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) 

plot_weather + geom_point(alpha = .5)
```

## Advanced scatterplot

Start with the same one and made it fancy

```{r}
weather_df %>% 
  ggplot(aes(tmin, tmax,color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE)
```


what about the 'aes' placement

```{r}
weather_df %>% 
  ggplot(aes(tmin, tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

facet same thing


```{r}
weather_df %>% 
  ggplot(aes(tmin, tmax,color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

combine some elements and tey a new plot

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```


**Write a code chain that starts with weather_df; focuses only on Central Park, converts temperatures to Fahrenheit, makes a scatterplot of min vs. max temperature, and overlays a linear regression line (using options in geom_smooth()).**

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```

Looks like there’s a pretty linear relationship between min and max temperatures in Central Park.

## some small notes

how many geoms have to exist?

You can have whatever geoms you want
```{r}
weather_df %>% 
  ggplot(aes(tmin,tmax,color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r}
weather_df %>% 
  ggplot(aes(tmin,tmax)) +
  geom_hex()
```

```{r}
weather_df %>% 
  ggplot(aes(tmin,tmax)) +
  geom_bin2d()
```

```{r}
weather_df %>% 
  ggplot(aes(tmin,tmax)) +
  geom_density_2d() + 
  geom_point(alpha = .3)
```

```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```

## univariate plots

histograms

```{r}
weather_df %>% 
  ggplot(aes(tmin)) + 
  geom_histogram()
```

add color

```{r}
weather_df %>% 
  ggplot(aes(tmin, fill = name)) + 
  geom_histogram(position = 'dodge')
```

```{r}
weather_df %>% 
  ggplot(aes(tmin, fill = name)) + 
  geom_histogram(position = 'dodge') +
  facet_grid(. ~name)
```

new geometry
```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
```

box plot
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

trendy plots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```

ridgeplots
```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```





